The Dynamics of Normalization Reweighting (target journal: Neuron)

### 2022-05-22 manuscript.Rmd
Update manuscript.Rmd

---
title: "The Dynamics of Normalization Reweighting (target journal: Neuron)"
author: "Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning, Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade"
date: "`r Sys.Date()`"
output: html_document
---

@@

runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
processraw <- 0  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours

# reasonably compact code to check which packages are installed, install the missing ones, and activate all
packagelist <- c('knitr','remotes','tictoc','R.matlab') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'osfr','FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}

targetelectrodes <- c('Oz','POz','O1','O2')

@@

```{r}

@@

abs(colMeans(mean5))
abs(colMeans(mean7))

@@

  ch <- match(toupper(targetelectrodes),toupper(electrodes),nomatch=0)

@@

@@

@@

@@

@@

@@

>>>>

---
title: 'The Dynamics of Normalization Reweighting (target journal: Neuron)'
author: Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice
  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning,
  Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes 
    toc: false   
    keep_tex: true
  word_document: default
  html_document: default
---

@@

runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
processraw <- 1  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours

# reasonably compact code to check which packages are installed, install the missing ones, and activate all
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'osfr','FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/figures/')){dir.create('temp/figures/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}

targetelectrodes <- c('Oz','POz','O1','O2')
# targetelectrodes <- c('PO8','PO6','PO5','PO7')

@@

```{r include=FALSE, results='hide'}

@@

@@

  ch <- match(targetelectrodes, electrodes) - 2

@@

save(file='temp/EEGsummary.RData',list=c('groupmeans','groupspecplot','groupwaveforms','groupspec','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))

if (runcode==1){
load('temp/EEGsummary.RData')

@@

pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 10)

@@

dev.off()

```{r EEGdata, fig.cap="E.", fig.align="center", echo=FALSE}

knitr::include_graphics('temp/figures/Fig3.pdf')

@@

save(file='temp/MEGsummary.RData',list=c('allspectra','allresps','allwaves','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
}

  load('temp/MEGsummary.RData')

@@

pdf("temp/figures/Fig4.pdf", bg="transparent", height = 10, width = 10)

@@

dev.off()
}

```{r MEGdata, fig.cap="E.", fig.align="center", echo=FALSE}

knitr::include_graphics('temp/figures/Fig4.pdf')
